Financialisation of commodities: co-movement behind-the-scenes

### 2022-04-27 docs/paper-remote.Rmd
update paper

```{r globals, include = FALSE}
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)

folder <- "literature_files"; dir.create(folder)
path <- paste(folder, "references.bib", sep = "/")
download.file(
  "https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", 
  paste(folder, "references.bib", sep = "/")
)
path <- paste(folder, "format.r", sep = "/")
download.file(
  "https://www.dropbox.com/s/a88duv7rhqq8aar/bookdown-functions-book-building.r?dl=1",
  path
)
source(path)

tables_font_size <- 9L
tables_collapse_rows_align <- "top"
tables_cut <- TRUE
tables_hline <- "major"

latex_options <- c("repeat_header")
latex_repeat_header_text <- "\\textit{(continued)}"
latex_repeat_header_method <- "replace"

html_font <- "Cambria"

html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
```

@@

```{r co-movement-stats-no-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (no regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)

caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. The results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 60) %>%
  pack_rows("equally weighted portfolios", 61, 64)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-stats-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)

caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "regime", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 120) %>%
  pack_rows("equally weighted portfolios", 121, 128)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-CHP-US}
table <- dplyr::filter(
  tables,
  analysis == "regressions - time series - US commodity returns ~ US commodity CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(regressor, dplyr::everything())

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently. The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("regressor", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-facts-US}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from US commodities"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption

colnames <- c("factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-picks}
table <- dplyr::filter(
  tables, analysis == "proportions"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$. The top eight commodities are selected as 'picks' for the corresponding factor and period. The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs. short) of its picking factor. The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors construction details are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "period", "pick", "long", "short")
align <- c("lllrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-correlations}
table <- dplyr::filter(
  tables, analysis == "average correlations (amongst factor picks)"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )

caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently. The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-picks-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - factor picks ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )

if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size,
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-UK-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - UK metals ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )

caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")

table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(
    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
  )

>>>>

```{r globals, include = FALSE}
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE)
folder <- "literature_files"; dir.create(folder)
path <- paste(folder, "references.bib", sep = "/")
download.file(
  "https://www.dropbox.com/s/htnd7o9nnkk8ng8/references.bib?dl=1", 
  paste(folder, "references.bib", sep = "/")
)
path <- paste(folder, "format.r", sep = "/")
download.file(
  "https://www.dropbox.com/s/a88duv7rhqq8aar/bookdown-functions-book-building.r?dl=1",
  path
)
source(path)
tables_font_size <- 9L
tables_collapse_rows_align <- "top"
tables_cut <- TRUE
tables_hline <- "major"
latex_options <- c("repeat_header")
latex_repeat_header_text <- "\\textit{(continued)}"
latex_repeat_header_method <- "replace"
html_font <- "Cambria"
html <- knitr::is_html_output(); latex <- knitr::is_latex_output()
```

@@

```{r co-movement-stats-no-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (no regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)
caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. The results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")
table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 60) %>%
  pack_rows("equally weighted portfolios", 61, 64) 
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-stats-regimes}
table <- dplyr::filter(tables, analysis == "descriptive statistics (regimes)") %>%
  dplyr::select(results) %>% tidyr::unnest(results)
caption <- "This table shows mean returns and volatility (sd) for the twenty four individual US commodities and the six LME metals considered in the study as well as for two equally weighted portfolios formed from the US commodities and the LME metals respectively across the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). Figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Mean values significant at the 1%, 5% and 10% level are marked with \\*\\*\\*, \\*\\* and \\* respectively. Aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("asset", "regime", "estimate", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")
table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) %>%
  pack_rows("individual commodities", 1, 120) %>%
  pack_rows("equally weighted portfolios", 121, 128)
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-CHP-US}
table <- dplyr::filter(
  tables,
  analysis == "regressions - time series - US commodity returns ~ US commodity CHP"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::select(regressor, dplyr::everything())
caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against relative changes in commercial hedging pressure (CHP) both at the individual (commodity CHP) and aggregate (aggregate CHP) levels independently. The results are reported for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("regressor", "sector", "subsector", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")
table <- kbl(
    table, booktabs = T, longtable = T, caption = caption, col.names = colnames, align = align
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline)
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-facts-US}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from US commodities"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )
caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four individual US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. The asset pool for the factor mimicking portfolio construction includes the twenty four US commodities. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("lllrrrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, col.names = colnames, align = align
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline) 
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-picks}
table <- dplyr::filter(
  tables, analysis == "proportions"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(period = stringr::str_replace_all(period, "present", "post-crisis")) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )
caption <- "This table shows the factor 'picks' for the market as well as the long-short factors for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018). For each factor and period the twenty four US commodities are regressed against the corresponding factor mimicking portfolio and ranked by $R^{2}$. The top eight commodities are selected as 'picks' for the corresponding factor and period. The table also shows the proportion of time, for each period, each individual pick lives on both legs (long vs. short) of its picking factor. The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors construction details are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "period", "pick", "long", "short")
align <- c("lllrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    ) 
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-correlations}
table <- dplyr::filter(
  tables, analysis == "average correlations (amongst factor picks)"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    factor = as.character(factor),
    factor = ifelse(factor == "OI nearby", "open interest", factor)
  )
caption <- "This table shows the average pairwise correlation amongst factor picks for each factor and period independently. The figures are shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor. Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llrrrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:2L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-picks-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - factor picks ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )
caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the various sets of factor picks are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the picks. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-US-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - US commodities ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )
caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the twenty four US commodities are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across all the twenty four commodities. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
    column_spec(1L, bold = TRUE) %>%
    collapse_rows(
      columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
    )
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size,
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```

@@

```{r co-movement-time-reg-UK-facts-picks}
table <- dplyr::filter(
  tables, 
  analysis == "regressions - time series - UK metals ~ factors from picks"
) %>% dplyr::select(results) %>% tidyr::unnest(results) %>%
  dplyr::mutate(
    dplyr::across(dplyr::contains("factor"), ~ as.character(.x)),
    dplyr::across(
      dplyr::contains("factor"), ~ ifelse(.x == "OI nearby", "open interest", .x)
    )
  )
caption <- "This table shows the average time series $R^{2}$ for models where the returns series for the six UK metals are regressed against factor mimicking portfolios independently with the resulting $R^{2}$ averaged across the six UK metals. For each picking factor and period, the market as well as the long-short factor mimicking portfolios are constructed from the corresponding set of factor picks. For each long-short factor (average CHP: CHP; open interest nearby growth: open interest; and term structure) the models are constructed with the factor itself (factor) as well as both legs independently (long vs. short). The results are reported in order for the market, CHP, open interest and term structure factors used as the picking factor, for the four periods of interest (past: 1997-2003; financialisation: 2004-2008; crisis: 2008-2013; post-crisis: 2013-2018) and shown independently for phases of aggregate backwardation (aggregate CHP $\\leq$ period median) and aggregate contango (aggregate CHP > period median). Factors as well as aggregate CHP construction and corresponding regime definitions along with details on the picking process are discussed in section \\@ref(co-movement-methods) while the results are discussed in section \\@ref(co-movement-results)."
caption <- if (latex) caption_latex(x = caption) else if (html) caption
colnames <- c("picking factor", "factor", "leg", "regime", "past", "financialisation", "crisis", "post-crisis")
align <- c("llllrrrr")
table <- kbl(
    table, longtable = T, booktabs = T, caption = caption, align = align, col.names = colnames
  ) %>%
  column_spec(1L, bold = TRUE) %>%
  collapse_rows(
    columns = 1L:3L, valign = tables_collapse_rows_align, longtable_clean_cut = tables_cut, latex_hline = tables_hline
  ) 
if (html) { kable_classic(table, full_width = TRUE, html_font = html_font) } else if (latex) {
   kable_classic(
     table, font_size = tables_font_size, 
     latex_options = latex_options, repeat_header_text = latex_repeat_header_text, repeat_header_method = latex_repeat_header_method
   )
}
```
